Many Analystis Project

### 2022-03-12 analysis-religious-final.Rmd
updated for publication

```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=TRUE, 
  #results="hide", 
  fig.width= 16,
  fig.height= 9)
```

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggraph")
library("lme4")
library("table1")
library("ggeffects")
library("kableExtra")
library("naniar") # missingness
library("Amelia")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
library("ggthemes")
=library("rstan")
library("brms")
library("bayesplot")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("emmeans")
library("splines")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
cite_packages(include_R = TRUE)

citation("daggity")
toBibtex(citation("ggdag"))
print(citation("EValue") , bibtex=TRUE)
```

@@

@@

```{r cache = TRUE}
# clean data:use informative names !
# note from Suzanne: 
# I do think it's actually a negative relation, as the anxiety item was reverse-coded (following the documentation from the WHO quality of life scale, from which the items were taken). This is indicated in the data documentation, but I can totally understand this got buried under all information that was provided. We tried to make the dataset as clean as possible since most teams just aggregated all well-being items (and the religiosity items). But in retrospect, this recoding did cause some confusion for a couple of teams that used only specific items (and prefered the ordinal scale). This is definitely something to take into account for future projects like this one.

df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    # NOOO revers scorred (1= religious, 2= not religious, 3=atheist) [R] So note that 3 = religious!!
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )
max(df$rel_EXTENTBELIEVEGOD)
max(df$rel_CHURCHFREQ)
length(unique(df$country))
table(df$country)
```

```{r}
# get data into shape

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    religious = as.integer(IS_RELIIGOUS), #(1= religious, 2= not religious, 3=atheist) [R]
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                religious,
                #   bg_s,
                denomination,
                wb_psychANXIETY)

@@

```{r}
lt <-table1::table1(~  denomination, data = d1, transpose=F)
lt
lt <-table1::table1(~ ch + religious + age + male + edu + ses + denomination |country, data = d1, transpose=F)
lt
kable(as.data.frame(lt), booktabs=TRUE, "latex")

nrow(dr)
```

@@

```{r}
library("ggdag")
library("dagitty")
dg1a <- dagify(
  anx  ~ belief + church  + age + male + ses + country ,
  belief ~ age + church + male + edu + ses  + church + country,
  church ~ age + male + edu + ses + country,
  ses ~ country + age + edu,
  edu ~ country + male + age, 
 # U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
 # latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
)     
dg1a
print( impliedConditionalIndependencies( dg1a ) )
print( adjustmentSets( dg1a,  "belief","anx" ) )

# 
# d0a <-ggdag::ggdag(dg1a, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("What if we were to assume distressing events increase belief in God?")
# d0a
# # graph adjustment sets
# 
# d1a<-ggdag::ggdag_adjustment_set(dg1a, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("If we assume distressing events affect belief and service we cannot estimate causal effects ")
# 
# d1a 
# 
# 
# # 
# dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed unmeasured causal effects of distressing experiences")
# 
# dp0
# # # graph adjustment sets
# # 
# #dp1<-ggdag::ggdag_adjustment_set(dg1, node_size = 14, text = FALSE, use_labels = "label") +
# #   theme(legend.position = "bottom") +
# #   theme_dag() + ggtitle("Adjustment sets for Belief in God")
# #dp1
# dp0
```
'
We adjust for: { church, country, male, ses } . Because we do not have information about education, we condition on the ladder

@@

# 
# ggdag::ggdag(dg2) + theme_dag()
# 
# nocause <- ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag() + labs(title = "Assume unmeasured distressing experience does not affect Belief or Service")
# nocause
# 
# dg0<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("Adjustment set for religious service
# assuming service does not change from distress")
# 
# dp0
#

@@

ggdag::ggdag(dpz) + theme_dag()
# 
# 
# # graph adjustment sets
dg1<-ggdag::ggdag_adjustment_set(dpz, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for religious belief
assuming belief does not change from distress")

@@

<!-- ```{r dg1, eval=FALSE} -->
<!-- # save graph -->
<!-- ggsave( -->
<!--   dg1, -->
<!--   path = here::here("Figs"), -->
<!--   width = 10, -->
<!--   height = 5, -->
<!--   units = "in", -->
<!--   filename = "dag_belief.jpg", -->
<!--   device = 'jpeg', -->
<!--   limitsize = FALSE, -->
<!--   dpi = 1200 -->
<!-- ) -->

<!-- ```{r dp0, eval=FALSE} -->
<!-- # save graph -->
<!-- ggsave( -->
<!--   dg1, -->
<!--   path = here::here("Figs"), -->
<!--   width = 10, -->
<!--   height = 5, -->
<!--   units = "in", -->
<!--   filename = "dag_church.jpg", -->
<!--   device = 'jpeg', -->
<!--   limitsize = FALSE, -->
<!--   dpi = 1200 -->
<!-- ) -->

@@

### Visualise missing data

```{r cache = TRUE}
library("naniar")
library(magick)
vis_miss(df) # substantial pattern of missingness in a few variables, 
df
df$wb_soc_3
dff<-df%>%
  select(-wb_soc_3)

miss_graph<- gg_miss_upset(dff)
miss_graphR <-image_ggplot(miss_graph)
# save graph
miss_graph

ggsave(miss_graph,
  path = here::here("figs"),
  width = 16,
  height = 9,
  units = "in",
  filename = "miss_graph.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

library(Amelia)

  # x is the longitudional dataframe (here 'd_3')
set.seed(1234)
prep <- d1 %>% # Remove what we do not need anymore
    arrange(country) %>%
    dplyr::select(anx,
                  ch,
                  age,
                  edu,
                  bg,
                  edu,
                  country,
                  male,
                  anx, 
                  ses)

table1::table1(~ ch |religious, data = d1)

We find there is substantial missingness in denomination. There is also missingness in ethnicity. Overall missingness is low in other indicators. However, 
Because missingness can introduce bias, we multiply impute responses.

## Model for belief

### Marginal structural model Church

@@

#d3<-complete(d2)
#saveRDS(d3,here::here("mods","d3"))
#d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         religious = factor(religious),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

## MICE ONLY RELIGIOUS
table(d1$religious)

# Check
d1r<- d1 %>%
  filter(religious == 3)

@@

@@

#check religious rumbers (1= religious, 2= not religious, 3=atheist) [R] So note that 3 = religious!!

@@

#saveRDS(d3,here::here("mods","d3r"))
#saveRDS(d3r,here::here("mods","d3r"))

d3 <-readRDS(here::here("mods","d3"))
d3r <-readRDS(here::here("mods","d3r"))

d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country),
         religious = as.factor(religious))

d4r<-d3r%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

library(ipw)

@@

max(d1p$ipwCH)

@@

# fine, well below 10
max(dr$ipwCH)
```

@@

```{r}
lt <-table1::table1(~ religious|ch_ord, data = dp)

kable(as.data.frame(lt), booktabs=TRUE, "latex")

nrow(dr)
```

### Simulation

```{r}
#\begin{lstlisting}[language=R]

set.seed(123)
sim_fun_A = function() {
  n <- 1000
  U <- rnorm(n, 1) # Unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + U)# rel id
  Y <- rnorm(n , - A*.2 + U + M*.1) #  distress reduced by attendance.

# simulate data
simdat_A <- data.frame(
  M = L, # rel id
  A = A, # rel service
  U = U, # distressing events (unmeasured)
  Y = Y ) # outcome

# average over outcomes: effect of religion is attenuated
parameters::pool_parameters(r_lm_A)

## Repeat but with no mediator in model
set.seed(123)
sim_fun_B = function() {
  n <- 1000
  U <- rnorm(n, 1) # Unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + U)# rel id + distress
  Y <- rnorm(n , - A *.2 + U + M*.1) #  distress reduced by attendance.

# simulate data
simdat_B <- data.frame(
  M = L, # rel id
  A = A, # rel service
  U = U, # distressing events (unmeasured)
  Y = Y ) # outcome

# Only exposure
sim_B <- lm(Y ~ A, data = simdat_A)
sim_B
}

# Replication 1000xs
r_lm_B <- NA
r_lm_B = replicate(100, sim_fun_B(), simplify = FALSE )

# average over outcomes: effect of religion is attenuated
parameters::pool_parameters(r_lm_B)

#\end{lstlisting}
```

@@

#saveRDS(dr, here::here("mods","dr"))

# saveRDS(d1p, here::here(
#   "mods","d1p"
# ))

b_orR <- brm(
  anx_s|weights(ipwCH) ~ mo(ch_ord) + (1 + mo(ch_ord) | country),
  data = dr,
   prior = c(
    prior(student_t(3, 0, .5), class = Intercept),
    prior(normal(-.05,.1), class = "b"),
    prior(dirichlet(1,1,1,1,1,1), class = "simo", coef = moch_ord1)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","b_orR")
)

@@

church_plot_R <-plot(ggeffects::ggemmeans(b_or, terms = "ch_ord")) +   xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot_R

### EEMEANS
 b_orR %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise")

@@

## include religion

```{r}
library(splines)

ipb_ch_ln_no_mediation <- geeglm(
  anx_s ~ ch,
  data = d1p,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)

@@

## Rel only

library(splines)
ipb_ch_lnR<- geeglm(
  anx_s ~ ch,
  data = dr,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
#saveRDS(ipb_ch_lnR, here::here("mods","ipb_ch_lnR"))
model_parameters(ipb_ch_lnR)

@@

# sensitivity
evalues.OLS(0.04, se = 0.01, sd = 1, delta = 1.4)

bias_plot(1.3009531, xmax = 6)

### Religous Only

@@

Adjusted GEE no weights

```{r}
# 
# ipb_bg_noweights <- geeglm(
#   anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
#   data = d1p,  
#   id = country,
#   corstr = "exchangeable"
# )
# saveRDS(ipb_bg_noweights, here::here("mods","ipb_bg_noweights"))
#

ipb_ch_noweights <- geeglm(
  anx_s ~ bs(ch_s) + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)
saveRDS(ipb_ch_noweights, here::here("mods","ipb_ch_noweights"))

msm_lmer <- lmer(
  anx_s ~ bs(ch_s) + age_s + edu_s + male_2 + ses_s +  (1+ ch_s|country),
  data = d1p, 
)
saveRDS(msm_lmer, here::here("mods","msm_lmer"))

msm_lmer_wg <- lmer(
  anx_s ~ bs(ch_s) + (1 + ch_s|country),
  weights = ipwCH,
  data = d1p
)
saveRDS(msm_lmer_wg, here::here("mods","msm_lmer_wg"))

# model_parameters(ipb_bg_noweights)
# model_parameters(ipb_bg_noweights)
# model_parameters(ipb_bg)
# model_parameters(ipb_bg)

model_parameters(ipb_ch_noweights)
model_parameters(ipb_ch)
model_parameters(ipb_ch)
model_parameters(msm_lmer)
model_parameters(msm_lmer_wg)

pred <- ggeffects::ggemmeans(msm_lmer_wg, terms = c("ch_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + 
  scale_y_continuous(limits=c(-.7,.7)) + 
  theme_classic() + ggtitle("") # title to be suppled

We note that the multi-level models give different estimates.

### Bayesian Church Attendaance

@@

#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc)

```
## Bayesian wieghted regression

```{r}
listout <- readRDS(here::here("mods","listout"))
modmc_wt_linear <- brm(
  anx_s|weights(ipwCH) ~ ch_s + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(normal(0, .1), class = Intercept),
    prior(normal(-.1,.1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","modmc_wt_linear")
)
#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc_wt_linear)

prior_summary(modmc_wt_linear)
summary(modmc_wt_linear)

library(brms)
library(splines)

@@

prior_summary(modmc_wt_priorStrong)

##### TeST PRIORS
modmc_wt_priorStrong_TEST <- brm(
  anx_s|weights(ipwCH) ~ bs(ch_s) + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(student_t(3, 0,.25), class = Intercept),
    prior(normal(-.05, .1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  sample_prior = "only",
  backend = "cmdstanr",
 file = here::here("mods","modmc_wt_priorStrong")
)

## WEAK PRIOR
modmc_wt_prior_weak <- brm(
  anx_s|weights(ipwCH) ~ bs(ch_s) + (1 + ch_s | country),
  data = d1p,
  prior = c(prior(normal(0, 1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  sample_prior = "only",
  backend = "cmdstanr"#,
 # file = here::here("mods","modmc_wt_prior")
)
```

@@

library(emmeans)
grand_mean

@@

church_plot <- plot(p0, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot

>>>>

```{r global_options, echo=FALSE, include = FALSE}
# setup
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=TRUE, 
  #results="hide", 
  fig.width= 16,
  fig.height= 9)
```

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions, not used
library("easystats")
library("ggraph")
library("lme4")
library("table1")
library("ggeffects")
library("kableExtra")
library("naniar") # missingness
library("Amelia")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
library("ggthemes")
=library("rstan")
library("brms")
library("bayesplot")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("emmeans")
library("splines")
library("magick")
library("tidyverse")
library("Amelia")
library("mice")

# Bayes options
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
cite_packages(include_R = TRUE)

# citations
# citation("daggity")
# toBibtex(citation("ggdag"))
# print(citation("EValue") , bibtex=TRUE)
```

@@

## Data import and set up

@@

```{r cache = TRUE}
# clean data:use informative names
df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    # NOOO revers scorred (1= religious, 2= not religious, 3=atheist) [R] So note that 3 = religious!!
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )
```

```{r}
# get data into shap
d1 <- df %>%
  dplyr::filter(
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    religious = as.integer(IS_RELIIGOUS), #(1= religious, 2= not religious, 3=atheist) [R]
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                edu,
                bg,
                edu,
                country,
                male,
                religious,
                denomination,
                wb_psychANXIETY)

@@

```{r}
lt <-table1::table1(~  denomination, data = d1, transpose=F)
lt <-table1::table1(~ ch + religious + age + male + edu + ses + denomination |country, data = d1, transpose=F)
lt
# Table for LaTeX
kable(as.data.frame(lt), booktabs=TRUE, "latex")
```

@@

```{r}
library("ggdag")
library("dagitty")
dg1a <- dagify(
  anx  ~ belief + church  + age + male + ses + country ,
  belief ~ age + church + male + edu + ses  + church + country,
  church ~ age + male + edu + ses + country,
  ses ~ country + age + edu,
  edu ~ country + male + age, 
 # U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
 # latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
)     
dg1a
print( impliedConditionalIndependencies( dg1a ) )
print( adjustmentSets( dg1a,  "belief","anx" ) )
```
'
We adjust for: { church, country, male, ses } . Because we do not have information about education, we condition on the ladder

@@

## Dag

@@

# # graph adjustment sets
dg1<-ggdag::ggdag_adjustment_set(dpz, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for religious belief
assuming belief does not change from distress")

@@

@@

Missing data can introduce selection bias.

We examine patterns of missingness and find substantial missingness in denominations

```{r cache = TRUE}
library("naniar")
vis_miss(df) # substantial pattern of missingness in a few variables,

# save missing file -- this does not work
# ggsave(miss_graph,
#   path = here::here("figs"),
#   width = 16,
#   height = 9,
#   units = "in",
#   filename = "miss_graph.jpg",
#   device = 'jpeg',
#   limitsize = FALSE,
#   dpi = 1200
# )
```

## Impute missing data

```{r cache = TRUE}
set.seed(1234)
prep <- d1 %>% # Remove what we do not need anymore
    arrange(country) %>%
    dplyr::select(anx,
                  ch,
                  age,
                  edu,
                  bg,
                  edu,
                  country,
                  male,
                  anx, 
                  ses)

# check
#table1::table1(~ ch |religious, data = d1)
```

## Impute missingness

@@

#d3<-complete(d2)
#saveRDS(d3,here::here("mods","d3"))
#d3 <-readRDS(here::here("mods","d3"))

d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         religious = factor(religious),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))
```

Imputation of the religion only dataset
```{r}
## MICE ONLY RELIGIOUS
d1r<- d1 %>%
  filter(religious == 3)

@@

# save
# saveRDS(d1p, here::here(
#   "mods","d1p"
# ))

@@

@@

# Save data 
#saveRDS(d3,here::here("mods","d3r"))
#saveRDS(d3r,here::here("mods","d3r"))

# read data
d3 <-readRDS(here::here("mods","d3"))
d3r <-readRDS(here::here("mods","d3r"))

# Select variables 
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country),
         religious = as.factor(religious))

d4r<-d3r%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))
```

Create inverse probability weights

```{r}
library(ipw)

@@

# check max value
#max(d1p$ipwCH)

@@

# fine, well below 10
#max(dr$ipwCH)
```

@@

```{r}
lt <-table1::table1(~ religious|ch_ord, data = dp)
lt
kable(as.data.frame(lt), booktabs=TRUE, "latex")
```

Relable variables

@@

# save
#saveRDS(dr, here::here("mods","dr"))
```

Bayesian model with strong priors

```{r}
b_orR <- brm(
  anx_s|weights(ipwCH) ~ mo(ch_ord) + (1 + mo(ch_ord) | country),
  data = dr,
   prior = c(
    prior(student_t(3, 0, .5), class = Intercept),
    prior(normal(-.05,.1), class = "b"),
    prior(dirichlet(1,1,1,1,1,1), class = "simo", coef = moch_ord1)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","b_orR")
)

@@

church_plot_R <-plot(ggeffects::ggemmeans(b_or, terms = "ch_ord")) +   xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot_R
```

Graphs

```{r}
### EEMEANS
 b_orR %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise")

@@

##  Gee models of various sorts

```{r}
library(splines)
ipb_ch_ln_no_mediation <- geeglm(
  anx_s ~ ch,
  data = d1p,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)

@@

# splines
library(splines)
ipb_ch_lnR<- geeglm(
  anx_s ~ ch,
  data = dr,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
#saveRDS(ipb_ch_lnR, here::here("mods","ipb_ch_lnR"))
model_parameters(ipb_ch_lnR)

@@

# sensitivity
evalues.OLS(0.04, se = 0.01, sd = 1, delta = 1.4)
bias_plot(1.3009531, xmax = 6)

### Religious Only

@@

### Bayesian Stratified Regression

Not used

@@

summary(modmc)
```

## Bayesian wieghted regression

```{r}
listout <- readRDS(here::here("mods","listout"))
modmc_wt_linear <- brm(
  anx_s|weights(ipwCH) ~ ch_s + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(normal(0, .1), class = Intercept),
    prior(normal(-.1,.1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","modmc_wt_linear")
)
#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc_wt_linear)
```

Priors used

```{r}
prior_summary(modmc_wt_linear)
```

Use of strong prior and splines

@@

prior_summary(modmc_wt_priorStrong)
```

Test strong priors on non-linear model

```{r}
##### TeST PRIORS
modmc_wt_priorStrong_TEST <- brm(
  anx_s|weights(ipwCH) ~ bs(ch_s) + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(student_t(3, 0,.25), class = Intercept),
    prior(normal(-.05, .1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  sample_prior = "only",
  backend = "cmdstanr",
 file = here::here("mods","modmc_wt_priorStrong")
)
```

Test a weaker prior.

```{r}
## Weak prior
modmc_wt_prior_weak <- brm(
  anx_s|weights(ipwCH) ~ bs(ch_s) + (1 + ch_s | country),
  data = d1p,
  prior = c(prior(normal(0, 1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  sample_prior = "only",
  backend = "cmdstanr"#,
 # file = here::here("mods","modmc_wt_prior")
)
```

## Graph

@@

@@

church_plot <- plot(p0, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot
```

### More graphs

```{r, cache = TRUE}
### EEMEANS
 modmc_wt_priorStrong %>% 
  emmeans(~ ch_s,
          at = list(ch_s = c(-0.8321022,2.23193),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise")
